---
title: "go_enrichment_exploration"
author: "Alice MacQueen"
date: "September 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## load data

```{r}
allgo <- read_csv(file = "5-EnrichmentAnalysis/FunctionsOfSignificantGOtermsForEachTrait.csv")
```
Ask Li: Are these p-values Bonferroni corrected already, or not?
```{r}
allgo %>%
  select(TRAIT, count, p.value, NAME) %>%
  group_by(NAME, TRAIT) %>%
  arrange(NAME, TRAIT)
 
allgo %>%
  group_by(NAME) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

allgo %>%
  select(TRAIT, count, p.value, NAME) %>%
  arrange(NAME)
```
response to oxidative stress 2 Al27, Cd111
nickel cation binding 2 Cu63, P31
metal ion transport (2) Sr88, Zn66
calcium ion binding 2 Ca44, K39
iron ion binding (3) K39, Mo98, Na23
oxidation-reduction process (3) Al27, K39, Rb855
peroxidase activity (3) Al27, Cd111, Mg26
protein ubiquitination (3) Ca44, K39, Mn55
heme binding (4) Al27, Cd111, Fe54, K39
oxidoreductase activity... (4) Cu63, Rb85, Fe54, K39, Mo98, Na23
DNA-binding transcription factor activity (6) Al27, Cu63, P31, Rb85, Sr88, Zn66
double-stranded DNA binding (5) Cu63, Fe54, Mg26, Mn55, P31
metal ion binding: Cd111 
metal ion transmembrane transporter activity Zn66
mitochondrion Cu63, Fe54, Mn55
Mn55: photosystem I
Ca44, Mn55: photosystem I reaction center
Mn55: response to metal ion
Mo98: endocytosis

Fe: cell wall
Al, Cu: cell wall biogenesis
