---
title: "go_enrichment_exploration"
author: "Alice MacQueen"
date: "September 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## load data

```{r}
allgo <- read_csv(file = "FunctionsOfSignificantGOterms.csv")

qtldf <- read_csv(file = "Functions&CandidateGenesForSignificantGOterms.csv")
pval <- read_csv(file = "SignificantGOtermsForTraits.csv")
```

```{r}
allgo <- pval %>%
  left_join(qtldf)

allgo

allgo %>%
  select(TRAIT, count, p.value, NAME) %>%
  group_by(NAME, TRAIT) %>%
  arrange(NAME, TRAIT)
 
allgo %>%
  group_by(NAME) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

allgo %>%
  select(TRAIT, count, p.value, NAME) %>%
  arrange(NAME)

allgo %>%
  filter(TRAIT == "Mo98") %>%
  group_by(QTL) %>%
  summarise(count = n())
  arrange(p.value)# %>%
  #select(TRAIT, count, p.value, NAME)

allgo %>%
  filter(TRAIT == "Mo98") %>%
  group_by(QTL, locusName, arabi.defline) %>%
  summarise(count = n())
  
  
allgo %>%
  arrange(p.value) %>%
  select(TRAIT, count, p.value, NAME)

```
response to oxidative stress 2 Al27, Cd111
nickel cation binding 2 Cu63, P31
metal ion transport (2) Sr88, Zn66
calcium ion binding 2 Ca44, K39
iron ion binding (3) K39, Mo98, Na23
oxidation-reduction process (3) Al27, K39, Rb855
peroxidase activity (3) Al27, Cd111, Mg26
protein ubiquitination (3) Ca44, K39, Mn55
heme binding (4) Al27, Cd111, Fe54, K39
oxidoreductase activity... (4) Cu63, Rb85, Fe54, K39, Mo98, Na23
DNA-binding transcription factor activity (6) Al27, Cu63, P31, Rb85, Sr88, Zn66
double-stranded DNA binding (5) Cu63, Fe54, Mg26, Mn55, P31
metal ion binding: Cd111 
metal ion transmembrane transporter activity Zn66
mitochondrion Cu63, Fe54, Mn55
Mn55: photosystem I
Ca44, Mn55: photosystem I reaction center
Mn55: response to metal ion
Mo98: endocytosis

Fe: cell wall
Al, Cu: cell wall biogenesis

strongest:
Sr88	45	1.674044e-31	nutrient reservoir activity	
Mn55	25	1.752972e-10	multicellular organism development	
Zn66	7	5.734243e-10	negative regulation of growth	
Al27	47	5.055185e-09	response to oxidative stress	
Al27	45	8.940713e-09	peroxidase activity	
Cu63	11	3.796033e-08	galactoside 2-alpha-L-fucosyltransferase activity	
Cu63	11	3.796033e-08	cell wall biogenesis	
Sr88	27	4.338558e-08	multicellular organism development	
Mn55	24	1.563897e-07	ubiquitin-dependent protein catabolic process	
Zn66	40	4.412713e-07	transferase activity, transferring hexosyl groups
Cu63	16	9.502358e-07	double-stranded DNA binding	
Rb85	6	1.785606e-06	pathogenesis	
Cu63	11	4.910442e-06	ADP binding	
Cu63	17	7.753797e-06	mitochondrion	
Sr88	27	7.761274e-06	ubiquitin-dependent protein catabolic process	
Mn55	71	1.190900e-05	nucleus	
Na23	19	1.638070e-05	iron ion binding	
Mn55	132	3.340187e-05	regulation of transcription, DNA-templated	
P31	366	3.658619e-05	regulation of transcription, DNA-templated	
Na23	3	3.751768e-05	carbonate dehydratase activity


Cytochromes P450 (CYPs) belong to the superfamily of proteins containing a heme cofactor and, therefore, are hemoproteins. CYPs use a variety of small and large molecules as substrates in enzymatic reactions. They are, in general, the terminal oxidase enzymes in electron transfer chains, broadly categorized as P450-containing systems.